Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-18 eqm_profiles.tex
write case 3 of eqm profile; will have to re-write proof of lemma 4

\vskip.2in
Period 1
\begin{enumerate}
	\item Patron would like $Q_{s1} \geq L_{s1}$ to prevent $c$ from incentivizing secessionists to Cede
		\begin{itemize}
			\item Equivalent to $q_{s1} + R_{p1} \geq l_{s1} + R_{c1}$ / $Q_{s0} + \mu + R_{p1} \geq L_{s0} + R_{c1}$ / $R_{p1} \geq R_{c1} - \left( Q_{s0} - \mu - L_{s0}\right)$
				\begin{itemize}
					\item $R_{c1} \leq \frac{\beta}{1-\de} \Rightarrow$ $R_{p1} \geq \frac{\beta}{1-\de} - \left( Q_{s0} - \mu - L_{s0}\right)$ allows the patron to ensure the original inequality
					\item Initial assumption means $R_{p1} \geq \frac{\beta}{1-\de} + \mu$ is a tighter condition
					\item Since patron is willing to pay up to $R_{p1} = \frac{\alpha}{1-\de}$, when $\frac{\alpha}{1-\de} \geq \frac{\beta}{1-\de} + \mu$, it will invest $R_{p1} = \frac{\beta}{1-\de} - \left( Q_{s0} - \mu - L_{s0}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. 
					  \begin{enumerate}
							\item If $R_{p1} + \left( Q_{s0} - \mu - L_{s0}\right) \geq \frac{\beta}{1-\de}$, $R_{c1} =0$. (SQ,SQ) is played and game continues.
							\item If instead $R_{p1} + \left( Q_{s0} - \mu - L_{s0}\right) < \frac{\beta}{1-\de}$ (i.e. assumption doesn't hold), $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right) + \ve$ to augment $l_{s1}$. Note optimal $R_{p1}$ in this case is 0.
								\begin{itemize}
									\item (SQ,Cede) is played and game ends
								\end{itemize}
						\end{enumerate}
				\end{itemize}
		\end{itemize}	
	\item Patron would like $L_{g1} > Q_{g1}$ to achieve recognition directly. Must invest to augment $l_{g1}$
		\begin{itemize}
			\item Equivalent to $l_{g1} + R_{p1} > q_{g1} + R_{c1}$ / $L_{g0} + R_{p1} > Q_{g0} + R_{c1}$ / $R_{p1} > R_{c1} + \left( Q_{g0} - L_{g0}\right)$
				\begin{itemize}
					\item $R_{c1} \leq \frac{\nu}{1-\de} \Rightarrow$ $R_{p1} > \frac{\nu}{1-\de} + \left( Q_{g0} - L_{g0}\right)$ allows the patron to ensure the original inequality
					\item Since patron is willing to pay up to $R_{p1} = \frac{\lambda +\mu + \beta}{1-\de}$, when $\frac{\lambda +\mu + \beta}{1-\de} \leq \frac{\nu}{1-\de}$, patron will invest 0 in $l_{g1}$. $R_{c1} = 0$ as well.
					\item If instead assumption 4 did not hold and $R_{p1} > \frac{\nu}{1-\de} + \left( Q_{g0} - L_{g0}\right)$, it will invest this amount to augment $l_{g1}$. Again, $R_{c1} = 0$. (Cede, SQ) is played and game ends.
				\end{itemize}
		\end{itemize}
	\item Patron might also want to instigate fighting. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de}$ is positive, invest in $w_{s1}$ to change $\omega_{s1}$. Will not invest in $w_{s1}$ when the quantity is non-positive.
		\begin{itemize}
			\item $c$ will counter up to $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}

>>>>

\vskip.2in
Period 1
\begin{enumerate}
	\item Patron would like $Q_{s1} \geq L_{s1}$ to prevent $c$ from incentivizing secessionists to Cede
		\begin{itemize}
			\item Equivalent to $q_{s1} + R_{p1} \geq l_{s1} + R_{c1}$ / $Q_{s0} + \mu + R_{p1} \geq L_{s0} + R_{c1}$ / $R_{p1} \geq R_{c1} - \left( Q_{s0} - \mu - L_{s0}\right)$
				\begin{itemize}
					\item $R_{c1} \leq \frac{\beta}{1-\de} \Rightarrow$ $R_{p1} \geq \frac{\beta}{1-\de} - \left( Q_{s0} - \mu - L_{s0}\right)$ allows the patron to ensure the original inequality
					\item Initial assumption means $R_{p1} \geq \frac{\beta}{1-\de} + \mu$ is a tighter condition
					\item Since patron is willing to pay up to $R_{p1} = \frac{\alpha}{1-\de}$, when $\frac{\alpha}{1-\de} \geq \frac{\beta}{1-\de} + \mu$, it will invest $R_{p1} = \frac{\beta}{1-\de} - \left( Q_{s0} - \mu - L_{s0}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. 
					  \begin{enumerate}
							\item If $R_{p1} + \left( Q_{s0} - \mu - L_{s0}\right) \geq \frac{\beta}{1-\de}$, $R_{c1} =0$. (SQ,SQ) is played and game continues.
							\item If instead $R_{p1} + \left( Q_{s0} - \mu - L_{s0}\right) < \frac{\beta}{1-\de}$ (i.e. assumption doesn't hold), $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right) + \ve$ to augment $l_{s1}$. Note optimal $R_{p1}$ in this case is 0.
								\begin{itemize}
									\item (SQ,Cede) is played and game ends
								\end{itemize}
						\end{enumerate}
				\end{itemize}
		\end{itemize}	
	\item Patron would like $L_{g1} > Q_{g1}$ to achieve recognition directly. Must invest to augment $l_{g1}$
		\begin{itemize}
			\item Equivalent to $l_{g1} + R_{p1} > q_{g1} + R_{c1}$ / $L_{g0} + R_{p1} > Q_{g0} + R_{c1}$ / $R_{p1} > R_{c1} + \left( Q_{g0} - L_{g0}\right)$
				\begin{itemize}
					\item $R_{c1} \leq \frac{\nu}{1-\de} \Rightarrow$ $R_{p1} > \frac{\nu}{1-\de} + \left( Q_{g0} - L_{g0}\right)$ allows the patron to ensure the original inequality
					\item Since patron is willing to pay up to $R_{p1} = \frac{\lambda +\mu + \beta}{1-\de}$, when $\frac{\lambda +\mu + \beta}{1-\de} \leq \frac{\nu}{1-\de}$, patron will invest 0 in $l_{g1}$. $R_{c1} = 0$ as well.
					\item If instead assumption 4 did not hold and $R_{p1} > \frac{\nu}{1-\de} + \left( Q_{g0} - L_{g0}\right)$, it will invest this amount to augment $l_{g1}$. Again, $R_{c1} = 0$. (Cede, SQ) is played and game ends.
				\end{itemize}
		\end{itemize}
	\item Patron might want to instigate fighting to have a $p_{1s}$ probability of achieving recognition indirectly. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de}$ is positive, invest in $w_{s1}$ to change $\omega_{s1}$. Will not invest when the quantity is non-positive. Inequality is $\omega_{s1} > Q_{s1}$
		\begin{itemize}
			\item $\omega_{s1} = -\zeta_{s}(1-\de) + W_{s1}p_{1s} + L_{s1}(1-p_{1s}) > Q_{s1}$
			\item $-\zeta_{s}(1-\de) + (W_{s0}+R_{p1})p_{1s} + L_{s0}(1-p_{1s}) > Q_{s0} - \mu + R_{c1}$
			\item $R_{p1}p_{1s} > R_{c1} - \mu + Q_{s0} - \left(-\zeta_{s}(1-\de) + W_{s0}p_{1s} + L_{s0}(1-p_{1s})\right)$
			\item $R_{c1} \leq \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$, so if $R_{p1}p_{1s} > \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s0} - \left(-\zeta_{s}(1-\de) + W_{s0}p_{1s} + L_{s0}(1-p_{1s})\right)$, $R_{c1}=0$ and (SQ,Fight) is played in third stage. Outcome depends on war lottery.
			\item Patron will spend at most $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) +\mu + \beta}{1 -\de}$
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}
